### 2017-01-06 paper/evaluation.tex
pass on text

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. We
used Maven as a reference due to its popularity on Java projects and
to automate our evaluation scripts. The rationale is that if the
string \emph{mvn} exists in the \emph{readme} file, it may represent a
Maven call (\eg, to compile or test the project).
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

@@

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 27 were unable to
fetch all dependencies (\eg, due to the usage of a private library),
and 131 were in an unstable revision. Our final set consists in
\numSubjs{} subjects.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test subjects,
and \emph{Python 3.4} to run our evaluation scripts. For replication,
all source artifacts are publicly available at \Fix{create gh-pages},
including supporting scripts (\eg, the script that test subjects and
generates the raw data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server). \Fix{Describe CPU isolation}

>>>>

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts.
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

@@

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects and 159 were in a
unstable revision. From these 159 unstable subjects, \Jbc{elaborate
what is unstable (eg, (1) how many could not resolve dependencies? (2)
how many could not compile sources and tests? (3) could not run tests
due to incompatible testing environment?}. Our final set consists in
\numSubjs{} testable subjects.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }\emph{git} to fetch
subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
subjects. Our evaluation scripts depends on \emph{Python 3.4} and
\emph{Bash} to execute.  For replication, all source artifacts are
publicly available at \Fix{create gh-pages}, including supporting
scripts (\eg, the script that test subjects and generates the raw
data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server). \Fix{Describe CPU isolation}
